Proposal Draft

### 2020-07-20 proposal draft .Rmd
Vix average score tables + score trace figures

```{r, message=FALSE}
#library(formattable)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(tsibble)
library(tsibbledata)
library(feasts)
library(normtest)
library(moments)
library(ggthemes)
library(ggpubr)
library(knitr)
library(kableExtra)
```

@@

>>>>

```{r, message=FALSE}
library(formattable)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(tsibble)
library(tsibbledata)
library(feasts)
library(normtest)
library(moments)
library(ggthemes)
library(ggpubr)
library(knitr)
library(kableExtra)
```

@@

```{r}
vix_table <- read.csv("vix_table.csv")
vix_table <- rename(vix_table, "In-sample optimizers" = Row,"FSR 10%" = FSR10, "FSR 20%"=FSR20, "FSR 80%"=FSR80,"FSR 90%"=FSR90)
vix_table$`In-sample optimizers`<-c("LS","CRPS","FSR 10%","FSR 20%","FSR 80%","FSR 90%")

vix_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"html",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"html",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR 10%` = cell_spec(format(`FSR 10%`,4),"html",bold = ifelse(`FSR 10%`==max(`FSR 10%`),TRUE,FALSE)),
    `FSR 20%` = cell_spec(format(`FSR 20%`,4),"html",bold = ifelse(`FSR 20%`==max(`FSR 20%`),TRUE,FALSE)),
    `FSR 80%` = cell_spec(format(`FSR 80%`,4),"html",bold = ifelse(`FSR 80%`==max(`FSR 80%`),TRUE,FALSE)),
    `FSR 90%` = cell_spec(format(`FSR 90%`,4),"html",bold = ifelse(`FSR 90%`==max(`FSR 90%`),TRUE,FALSE))
  ) %>%
  kable("html",escape = F) %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table ?: Average scores for VIX"=7))
```

```{r,fig.width=10,fig.height=5}
# to compress all the calculated plotting average scores together in the same df 
trace_fsr10 <- read.csv("vixfsr10.csv")
trace_fsr20 <- read.csv("vixfsr20.csv")
trace_10ls <- read.csv("vixfsr10_ls.csv")
trace_10crps <- read.csv("vixfsr10_crps.csv")

fsr10 <- fsr10 %>% mutate(Date = vix$Date[1001:6000])

# plot scores --- upper tail 
trace_fsr90 <- read.csv("vixfsr90.csv")
trace_fsr80 <- read.csv("vixfsr80.csv")
trace_90ls <- read.csv("vixfsr90_ls.csv")
trace_90crps <- read.csv("vixfsr90_crps.csv")

fsr90 <- fsr90 %>% mutate(Date = vix$Date[1001:6000])

# put two plots side by side 
ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure ?(a) Lower Tail","Figure ?(b) Upper Tail"))
